The onset of hydrodynamically driven waving of marine grass in flow

### 2014-09-26 Paper/grass.tex
Fix abstract and title, and ready to send out!

\begin{document}
\title{The onset of of hydrodynamically driven waving of marine grass in flow}
\author{Ravi Singh}
\affiliation{Brown University, Providence RI 02912 USA}
\author{L. Mahadevan}
\affiliation{Harvard University, Cambridge MA 02138 USA}
\author{M. M. Bandi\thanks{work performed while visiting Brown University}}
\affiliation{Collective Interactions Unit, OIST Graduate University, 1919-1 Tancha, Onna-son, Okinawa, Japan 904-0495}
\author{Amala Mahadevan}
\affiliation{Woods Hold Institute of Oceanography, Woods Hole MA USA}
\author{Shreyas Mandre}
\affiliation{Brown University, Providence RI 02912 USA}

@@

We show that the threshold flow condition for the spontaneous waving of marine grass arises due to the drag exerted by the vegetation on the flow. 
We show this by developing a self-consistent model of the flow past rigid vegetation. 
Linear stability analysis of the steady flow resulting from this model naturally leads to the threshold condition, and explains its mechanistic origin. 
Asymptotic analysis of the model for dense grass reveals two unstable modes. 
One of these modes shares many common features with the Kelvin-Helmholtz instability, but is demonstrated to be different from it. 

@@

>>>>

\begin{document}
\title{The onset of hydrodynamically driven waving of marine grass in flow}
\author{Ravi Singh}
\affiliation{Brown University, Providence RI 02912 USA}
\author{L. Mahadevan}
\affiliation{Harvard University, Cambridge MA 02138 USA}
\author{M. M. Bandi\thanks{work performed while visiting Brown University}}
\affiliation{Collective Interactions Unit, OIST Graduate University, 1919-1 Tancha, Onna-son, Okinawa, Japan 904-0495}
\author{Amala Mahadevan}
\affiliation{Woods Hole Institute of Oceanography, Woods Hole MA USA}
\author{Shreyas Mandre}
\affiliation{Brown University, Providence RI 02912 USA}

@@

We develop a self-consistent model of the flow past rigid vegetation, where the vegetation is represented by a continuum drag field.
To explain the onset of spontaneous waving, we perform a linear stability analysis of the steady flow resulting from this model.
We show that a threshold flow condition for the spontaneous waving of marine grass arises naturally in this framework due to the drag exerted by the vegetation on the flow. 
Beyond the threshold, we find two unstable modes; first is localized in a boundary layer near the canopy top, and second which spans the whole water column.
The first mode shares many common features with the Kelvin-Helmholtz instability, but is demonstrated to be different from it. 

@@

% Asymptotic analysis of the model for dense grass reveals two unstable modes. 
% We show this by  
%  naturally leads to the threshold condition, and explains its mechanistic origin. 
